### 2020-10-13 latex/images/vlp_energy_in_out.tex
Updated labels on all VLP images

\begin{document}
\begin{tikzpicture}
% Set the underline{l} and overline{l} positions
\pgfmathsetmacro{\lu}{2}
\pgfmathsetmacro{\lb}{4}
\pgfmathsetmacro{\dl}{(\lb - \lu)/2}
\pgfmathsetmacro{\lavg}{(\lb + \lu)/2}
% Define the figure
\begin{axis}[ 
 axis line style = thick,
 % Set the axes to be centered nicely
 axis x line = center, 
 axis y line = middle,
 xlabel = $\theta$, 
 x label style={at={(axis description cs:1.08,0)},anchor = east},
 xmin = -3.1415, xmax = 3.1415,
 ylabel = $l(\theta)$,
 y label style={at={(axis description cs:0.5,1.1)},anchor = north}, 
 ymin = 0, ymax = 5,
 % Custom tick labels at specified positions
 xticklabels = {$-\pi$, $-\frac{\pi}{2}$, $0$, $\frac{\pi}{2}$, $\pi$},
 xtick={-3.1415, -1.571, 0, 1.571, 3.1415},
 yticklabels = {$\underline{l}$,$l_{avg}$,$\overline{l}$},
 ytick = {\lu,\lavg,\lb}, % Choose the plot values for underline{l} and overline{l}
 % Move the \overbar{l} label to the right
 yticklabel style={xshift={(\ticknum==1)*(1cm)},yshift={(\ticknum==0)*(-0.25cm)+(\ticknum==1)*(0.25cm) + (\ticknum==2)*(0.25cm)}},
 legend pos=south east,
 axis on top
]
    % Add named boundaries for each of the blocked regions. We use "forget
    % plot" so they don't appear on the legend
    \addplot[draw=none, forget plot, name path global=I1U,domain=-pi:(-pi/2)]{\lu};
    \addplot[draw=none, forget plot, name path global=I2U,domain=(-pi/2):0]{\lu};
    \addplot[draw=none, forget plot, name path global=I3U,domain=0:(pi/2)]{\lu};
    \addplot[draw=none, forget plot, name path global=I4U,domain=(pi/2):pi]{\lu};

>>>>

\begin{document}
\begin{tikzpicture}
% Set the underline{l} and overline{l} positions
\pgfmathsetmacro{\lu}{2}
\pgfmathsetmacro{\lb}{4}
\pgfmathsetmacro{\dl}{(\lb - \lu)/2}
\pgfmathsetmacro{\lavg}{(\lb + \lu)/2}
% Define the figure
\begin{axis}[ 
 axis line style = thick,
 % Set the axes to be centered nicely
 axis x line = center, 
 axis y line = middle,
 xlabel = $\theta$, 
 x label style={at={(axis description cs:1.08,0)},anchor = east},
 xmin = -3.1415, xmax = 3.1415,
 ylabel = $l$,
 y label style={at={(axis description cs:0.5,1.1)},anchor = north}, 
 ymin = 0, ymax = 5,
 % Custom tick labels at specified positions
 xticklabels = {$-\pi$, $-\frac{\pi}{2}$, $0$, $\frac{\pi}{2}$, $\pi$},
 xtick={-3.1415, -1.571, 0, 1.571, 3.1415},
 yticklabels = {$\underline{l}$,$l_{avg}$,$\overline{l}$},
 ytick = {\lu,\lavg,\lb}, % Choose the plot values for underline{l} and overline{l}
 % Move the \overbar{l} label to the right
 yticklabel style={xshift={(\ticknum==1)*(1cm)},yshift={(\ticknum==0)*(-0.25cm)+(\ticknum==1)*(0.25cm) + (\ticknum==2)*(0.25cm)}},
 legend pos=south east,
 axis on top
]
    % Add named boundaries for each of the blocked regions. We use "forget
    % plot" so they don't appear on the legend
    \addplot[draw=none, forget plot, name path global=I1U,domain=-pi:(-pi/2)]{\lu};
    \addplot[draw=none, forget plot, name path global=I2U,domain=(-pi/2):0]{\lu};
    \addplot[draw=none, forget plot, name path global=I3U,domain=0:(pi/2)]{\lu};
    \addplot[draw=none, forget plot, name path global=I4U,domain=(pi/2):pi]{\lu};
